Data preprocessing

### 2022-04-25 dev/work/boston_housing.qmd
Fun with latex templates

```{julia}
opt = ADAM()
loss_type = :logitbinarycrossentropy
run = false
if run
    K = 50
    𝓜 = Models.build_ensemble(K,kw=(input_dim=size(X)[1], n_hidden=100));
    𝓜, anim = Models.forward(𝓜, data, opt, n_epochs=30, plot_every=10, loss_type=loss_type); # fit the ensemble
    Models.save_ensemble(𝓜, root=joinpath(output_folder, "ensemble")) # save to disk
    gif(anim, joinpath(www_folder, "ensemble_loss.gif"), fps=25);
end
```

@@

```{julia}
𝓜 = Models.load_ensemble(root=joinpath(output_folder, "ensemble"))
𝑴 = Models.FittedEnsemble(𝓜, opt, loss_type);
```

>>>>

```{julia}
opt = ADAM()
loss_type = :logitbinarycrossentropy
run = false
if run
    K = 50
    ensemble = Models.build_ensemble(K,kw=(input_dim=size(X)[1], n_hidden=100));
    ensemble, anim = Models.forward(ensemble, data, opt, n_epochs=30, plot_every=10, loss_type=loss_type); # fit the ensemble
    Models.save_ensemble(ensemble, root=joinpath(output_folder, "ensemble")) # save to disk
    gif(anim, joinpath(www_folder, "ensemble_loss.gif"), fps=25);
end
```

@@

```{julia}
ensemble = Models.load_ensemble(root=joinpath(output_folder, "ensemble"))
𝑴 = Models.FittedEnsemble(ensemble, opt, loss_type);
```

### 2022-04-25 dev/work/synthetic_endogenous_shifts.qmd
Fun with latex templates

```{julia}
using Pkg; Pkg.activate("..")
```

```{julia}
include("../src/load.jl")
using AlgorithmicRecourse
using CSV, DataFrames
using LinearAlgebra;
using Distributions;
using Images, FileIO;
using Plots, PlotThemes
theme(:wong)
using Logging
disable_logging(Logging.Info)
output_folder = "output/synthetic"
www_folder = "www/synthetic"
using Base.Filesystem: joinpath
```

@@

```{julia}
opt = ADAM()
loss_type = :logitbinarycrossentropy
run = false
if run
    K = 50
    𝓜 = Models.build_ensemble(K,kw=(input_dim=size(X')[1], n_hidden=100));
    𝓜, anim = Models.forward(𝓜, data, opt, n_epochs=10, plot_every=10, loss_type=loss_type, τ=1.1); # fit the ensemble
    Models.save_ensemble(𝓜, root=joinpath(output_folder, "ensemble")) # save to disk
    gif(anim, joinpath(www_folder, "ensemble_loss.gif"), fps=25);
end
```

```{julia}
𝓜 = Models.load_ensemble(root=joinpath(output_folder, "ensemble"))
𝑴 = Models.FittedEnsemble(𝓜, opt, loss_type)
models = (Bayesian=𝑴, Plugin=𝑴ₙₙ);
```

>>>>

```{julia}
include("dev/utils.jl")
using CounterfactualExplanations, CSV, DataFrames, LinearAlgebra, Distributions, Images, FileIO, Plots, PlotThemes
using Base.Filesystem: joinpath
theme(:wong)
using Logging
disable_logging(Logging.Info)
output_folder = "output/synthetic"
www_folder = "www/synthetic"
```

@@

```{julia}
opt = ADAM()
loss_type = :logitbinarycrossentropy
run = false
if run
    K = 50
    ensemble = Models.build_ensemble(K,kw=(input_dim=size(X')[1], n_hidden=100));
    ensemble, anim = Models.forward(ensemble, data, opt, n_epochs=10, plot_every=10, loss_type=loss_type, τ=1.1); # fit the ensemble
    Models.save_ensemble(ensemble, root=joinpath(output_folder, "ensemble")) # save to disk
    gif(anim, joinpath(www_folder, "ensemble_loss.gif"), fps=25);
end
```

```{julia}
ensemble = Models.load_ensemble(root=joinpath(output_folder, "ensemble"))
𝑴 = Models.FittedEnsemble(ensemble, opt, loss_type)
models = (Bayesian=𝑴, Plugin=𝑴ₙₙ);
```
